Data Preparation - Course Catalogues

### 2019-04-16 Data Preparation - Course Catalogues.Rmd

course_code_UCM_UCV_MSP <- c("COR", "HUM", "SCI", "SSC", "SKI", "PRO", "UGR", "CAP", # UCM
                         "VCO", "VSC", "VSS", "VSK", "VPR", "VCA", # UCV
                         "BIO", "CHE", "MAT", "PHY", "NEU", "INT", "PRA" #MSP
                         ) %>% collapse_or
overview_start  <- function(string) string %>% extract_id_course %>% str_detect(pattern = course_code_UCM_UCV_MSP) # simplify with %in% course_code_UCM
```

@@

  # paste current page and following page (`lead(page)`) if overview is two page long
  transmute(
    text        = list(page, lead(page)) %>% pmap_chr(paste_if_2_page_overview),
    `Course ID` = text %>% extract_id_course) %>%
    mutate(department  = ID) %>%
    filter(!is.na(text))

>>>>

course_code_UCM_UCV_MSP <- c("COR", "HUM", "SCI", "SSC", "SKI", "PRO", "UGR", "CAP", # UCM
                         "VCO", "VSC", "VSS", "VSK", "VPR", "VCA", # UCV
                         "BIO", "CHE", "MAT", "PHY", "NEU", "INT", "PRA" #MSP
                         ) %>% collapse_or
overview_start  <- function(string) string %>% extract_id_course %>% str_detect(pattern = course_code_UCM_UCV_MSP) # simplify with %in% course_code_UCM

titles_end_UCM_UCV_MSP <- c("1000", "2000", "3000", #UCV
                            "Course coordinators?",    #UCM, MSP
                            "Coordinator", "PLEASE NOTE:", "Note:" #MSP
                            ) %>% collapse_or

title_end_location <- function(string) str_locate(string, titles_end_UCM_UCV_MSP) %>% .[,1]
extract_course_title <- function(string) str_sub(string, 9, title_end_location(string)-2)
```

@@

  # paste current page and following page (`lead(page)`) if overview is two page long
  transmute(
    text           = list(page, lead(page)) %>% pmap_chr(paste_if_2_page_overview),
    `Course ID`    = text %>% extract_id_course,
    `Course Title` = text %>% extract_course_title) %>%
    mutate(department  = ID) %>%
    filter(!is.na(text))
